**The status of the microbial census: an update**

### 2015-11-18 results/tables/build_table_1.Rmd
Fix label ordering; add OTU coverage

fine <- c("", "Brackish", "Brackish sediment", "Freshwater", "Freshwater sediment", "Hydrothermal vent", "Ice", "Marine", "Marine sediment", "Other", "Digesters", "Food-associated", "Industrial/mining", "Other", "Pollution associated", "Other", "Root", "Surface", "Agriculture", "Desert", "Other", "Permafrost", "Arthropod", "Other invertebrate", "Other", "Vertebrate", "", "", "")

@@

get_coverage <- function(x, db){
	if(x=="NA"){
		x_table <- table(db[is.na(db$category), "otu"])
	} else if(x == "total") {
		x_table <- table(db[, "otu"])
	} else {
		x_table <- table(db[db$category==x, "otu"])
	}

@@

bact_count <- table(bact$category)[abbreviation]
bact_count[is.na(bact_count)] <- 0
bact_count <- c(bact_count, nrow(bact) - sum(bact_count))
bact_count <- format(c(bact_count, nrow(bact)), big.mark=',')
bact_sobs <- format(sapply(c(abbreviation, "NA", "total"), get_sobs, bact), big.mark=',')
bact_coverage <- format(sapply(c(abbreviation, "NA", "total"), get_coverage, bact), nsmall=1, digits=3)

arch_count <- table(arch$category)[abbreviation]
arch_count[is.na(arch_count)] <- 0
arch_count <- c(arch_count, nrow(arch) - sum(arch_count))
arch_count <- format(c(arch_count, nrow(arch)), big.mark=',')
arch_sobs <- format(sapply(c(abbreviation, "NA", "total"), get_sobs, arch), big.mark=',')
arch_coverage <- format(sapply(c(abbreviation, "NA", "total"), get_coverage, arch), nsmall=1, digits=3)

#abbreviation <- c(abbreviation, "", "")
composite <- cbind(coarse, fine, bact_count, bact_sobs, bact_coverage, arch_count, arch_sobs, arch_coverage)
composite <- rbind(c("", "", "Sequences", "OTUs", "Coverage (%)", "Sequences", "OTUs", "Coverage (%)"), composite)

@@

addtorow <- list(pos=list(0, 1),
				command=c('\\multirow{2}{*}{Coarse} & \\multirow{2}{*}{Fine} & \\multicolumn{3}{c}{Bacterial} & \\multicolumn{3}{c}{Archaeal} \\\\ \\cmidrule(r){3-5}	\\cmidrule(r){6-8}', '\\hline '))

align(composite) <- "lllcccccc"
print(composite, add.to.row=addtorow, include.rownames=FALSE, include.colnames=FALSE, hline.after = c(-1,nrow(composite)-1, nrow(composite)), comment=FALSE, size="small")
```

>>>>

fine <- c("", "Brackish", "Brackish sediment", "Freshwater", "Freshwater sediment", "Hydrothermal vent", "Ice", "Marine", "Marine sediment", "Other", "Digesters", "Food-associated", "Industrial/mining", "Pollution associated", "Other", "Root", "Surface", "Other", "Agriculture", "Desert", "Permafrost", "Other", "Arthropod", "Other invertebrate", "Vertebrate", "Other", "", "", "")

@@

get_goods_coverage <- function(x, db){
	if(x=="NA"){
		x_table <- table(db[is.na(db$category), "otu"])
	} else if(x == "total") {
		x_table <- table(db[, "otu"])
	} else {
		x_table <- table(db[db$category==x, "otu"])
	}

@@

get_schloss_coverage <- function(x, db){
	if(x=="NA"){
		x_table <- table(db[is.na(db$category), "otu"])
	} else if(x == "total") {
		x_table <- table(db[, "otu"])
	} else {
		x_table <- table(db[db$category==x, "otu"])
	}

	singletons <- sum(x_table == 1)
	total_otus <- length(x_table)

	if(total_otus != 0){
		100*(1-singletons/total_otus)
	} else {
		NA
	}

bact_count <- table(bact$category)[abbreviation]
bact_count[is.na(bact_count)] <- 0
bact_count <- c(bact_count, nrow(bact) - sum(bact_count))
bact_count <- format(c(bact_count, nrow(bact)), big.mark=',')
bact_sobs <- format(sapply(c(abbreviation, "NA", "total"), get_sobs, bact), big.mark=',')
bact_good_coverage <- format(sapply(c(abbreviation, "NA", "total"), get_goods_coverage, bact), nsmall=1, digits=3)
bact_schloss_coverage <- format(sapply(c(abbreviation, "NA", "total"), get_schloss_coverage, bact), nsmall=1, digits=3)

arch_count <- table(arch$category)[abbreviation]
arch_count[is.na(arch_count)] <- 0
arch_count <- c(arch_count, nrow(arch) - sum(arch_count))
arch_count <- format(c(arch_count, nrow(arch)), big.mark=',')
arch_sobs <- format(sapply(c(abbreviation, "NA", "total"), get_sobs, arch), big.mark=',')
arch_good_coverage <- format(sapply(c(abbreviation, "NA", "total"), get_goods_coverage, arch), nsmall=1, digits=3)
arch_schloss_coverage <- format(sapply(c(abbreviation, "NA", "total"), get_schloss_coverage, arch), nsmall=1, digits=3)

#abbreviation <- c(abbreviation, "", "")
composite <- cbind(coarse, fine, bact_count, bact_sobs, bact_good_coverage, bact_schloss_coverage, arch_count, arch_sobs, arch_good_coverage, arch_schloss_coverage)
composite <- rbind(c("", "", "Sequences", "OTUs", "Seq.", "OTU", "Sequences", "OTUs", "Seq.", "OTU"), composite)

@@

addtorow <- list(pos=list(0, 1),
				command=c('\\multirow{2}{*}{Coarse} & \\multirow{2}{*}{Fine} & \\multicolumn{4}{c}{Bacterial} & \\multicolumn{4}{c}{Archaeal} \\\\ \\cmidrule(r){3-6}	\\cmidrule(r){7-10}', '\\hline '))

align(composite) <- "lllcccccccc"
print(composite, add.to.row=addtorow, include.rownames=FALSE, include.colnames=FALSE, hline.after = c(-1,nrow(composite)-1, nrow(composite)), comment=FALSE, size="small")
```
